Memory-aware Adaptive Scheduling of Scientific Workflows on Heterogeneous Architectures\\

### 2025-03-11 main.tex
rewrote the text about successes of with/without recomputation in VI.C

\subsection{Dynamic experiments on the memory-constrained cluster}
\label{sec.expe.dyn}
\new{In this section, we try to assess the advantage of the dynamic approach.
To this end, we compare the makespans of executions with and without recomputation.}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants \new{obtain a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests,
\new{i.e., when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments end with a valid makespan in case of no recomputation.
Hence, these workflows require so few resources that
\new{the devations do not invalidate their scheduler. However, there is also nothing to be gained by rescheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.

In case of \heftmm, all $290$\todo{SK: check!} workflows can be scheduled initially and all the schedules remain valid until the end,
\new{when new schedules are computed in a dynamic way. Only}  
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.

\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end.
$50$ experiments are successful without recomputation, a rate of $35\%$ out of all successful final schedules.

\heftbl keeps $105$ schedules valid until the end out of $110$ initially valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.

>>>>

\subsection{Dynamic experiments on the memory-constrained cluster}
\label{sec.expe.dyn}
\new{In this section, we try to assess the advantage of the dynamic approach.
To this end, we compare the makespans of executions with and without recomputation.}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160
(290 experiments for each of the 3 heuristics and the baseline \heft)
 \new{obtain a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid \new{until the end of an execution with recomputation},
\new{i.e., the schedule is still valid when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments end \new{valid in case of no recomputation, i.e. when following the initial schedule without ever recomputing it}.
Hence, these workflows require so few resources that
\new{the devations do not invalidate their schedules. However, there is also nothing to be gained by rescheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.

In case of \heftmm, all $290$ workflows can be scheduled initially \new{(static case)} and all these schedules remain valid until the end,
\new{when new schedules are computed in a dynamic way. However, only}
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.

\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end \new{when new schedules are computed in a dynamic way.}
$50$ experiments \new{remain} successful \new{when following the original schedule} without recomputation, a rate of $35\%$ out of all successful final schedules.

\heftbl keeps $105$ schedules valid until the end out of $110$ initial \new{(static)} valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.
